Your Wonderful Project Topic

### 2021-12-08 Paper/main.tex
finish dataset process

Our project dataset is FIFA 2019 players attributes dataset, which is collected
from Kaggle. This dataset includes 89 attributes of a soccer player, and our
project only uses some of these attributes concerning only player capability.
Besides, considering that goalkeepers have a totally different set of capability
metrics compared with other players, we will only consider data records of nongoalkeepers in our model.\\
Now we beginning the data processing.
There are 18206 players for which 89 features each are provided. Fristly, we should drop the duplicate entries. 
Then we check the variables: 
\begin{center}
$ID, Name, Age, Photo, Nationality, Flag, Overall, Potential, Club, Club Logo, Value,$\\ 
$Wage, Special, Preferred Foot, International Reputation, Weak Foot, Skill Moves,$\\
$Work Rate, Body Type, Real Face, Position, Jersey Number, $\\
$Joined, Loaned From, Contract Valid Until,Height, Weight,$\\
$LS, ST, RS, LW, LF, CF, RF, RW, LAM, CAM, RAM, LM, LCM, CM,$\\
$RCM, RM, LWB, LDM, CDM, RDM, RWB, LB, LCB, CB, RCB, RB,$ \\
$Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,$\\ 
$Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$\\ 
$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,$\\ $LongShots, Aggression, Interceptions, Positioning, Vision, Penalties, Composure,$\\ $Marking, StandingTackle, SlidingTackle,$\\
$GKDiving, GKHandling, GKKicking, GKPositioning,
GKReflexes, Release Clause$
\end{center}
\\
We have to delete the missing value which will distrubing our model. 

@@

@@

@@

Conserning these missing value we have belowing comments:\\
(i) Since a big chunk of players are not loaned to other clubs, hence there are $16943$ missing values out of $18206$ i.e. they play for their own club.\\
(ii) There is a consistency $(11.45\%)$ in missing values for the position (they play on), this needs to be explored.\\
(iii) Release clause, joined, contract valid until, club, position, jersey number have missing values and need to be explored.\\
(iv) There is a consistency $(0.26\%)$ in missing values for the players rating attributes.

>>>>

\subsection{Dateset overall}

Our project dataset is FIFA 2019 players attributes dataset, which is collected
from Kaggle. This dataset includes 89 attributes of a soccer player, and our
project only uses some of these attributes concerning only player capability.
Besides, considering that goalkeepers have a totally different set of capability
metrics compared with other players, we will only consider data records of nongoalkeepers in our model.

\subsection{Data processing}

Now we beginning the data processing.
There are 18206 players for which 89 features each are provided. Firstly, we should drop the duplicate entries. 
Then we check the variables: 
\begin{center}
$ID, Name, Age, Photo, Nationality, Flag, Overall, Potential, Club, Club Logo, Value,$\\ 
$Wage, Special, Preferred Foot, International Reputation, Weak Foot, Skill Moves,$\\
$Work Rate, Body Type, Real Face, Position, Jersey Number, $\\
$Joined, Loaned From, Contract Valid Until,Height, Weight,$\\
$LS, ST, RS, LW, LF, CF, RF, RW, LAM, CAM, RAM, LM, LCM, CM,$\\
$RCM, RM, LWB, LDM, CDM, RDM, RWB, LB, LCB, CB, RCB, RB,$ \\
$Crossing, Finishing, HeadingAccuracy, ShortPassing, Volleys, Dribbling,$\\ 
$Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$\\ 
$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength,$\\ $LongShots, Aggression, Interceptions, Positioning, Vision, Penalties, Composure,$\\ $Marking, StandingTackle, SlidingTackle,$\\
$GKDiving, GKHandling, GKKicking, GKPositioning,
GKReflexes, Release Clause$
\end{center}
\\
Now we have to delete the missing value which will distrubing our model.

@@

\centering

@@

\caption{Missing value percent}

@@

\newpage

Considering these missing value we have below comments:
\begin{itemize}
    \item Since a big chunk of players are not loaned to other clubs, hence there are $16943$ missing values out of $18206$ i.e. they play for their own club.
    \item There is a consistency $(11.45\%)$ in missing values for the position (they play on), this needs to be explored.
    \item Release clause, joined, contract valid until, club, position, jersey number have missing values and need to be explored.
    \item There is a consistency $(0.26\%)$ in missing values for the players rating attributes.
\end{itemize}
\\
Now we will drop unnecessary columns, which can address the problem simply, reference the FIFA official guideline (https://www.fifauteam.com/fifa-19-attributes-guide/). we only keep significant values that have highly contributed to the model.

\begin{center}
$Age, Overall, Potential, Weak Foot, Position, Crossing, Finishing, HeadingAccuracy,$ \\
$ShortPassing, Volleys, Dribbling, Curve, FKAccuracy, LongPassing, BallControl, Acceleration,$ \\
$SprintSpeed, Agility, Reactions, Balance, ShotPower, Jumping, Stamina, Strength, LongShots,$\\
$Aggression, Interceptions, Positioning, Vision, Penalties, Composure, Marking, StandingTackle,$ \\
$SlidingTackle, GKDiving, GKHandling, GKKicking, GKPositioning, GKReflexes$
\end{center}

We have to delete the missing value which will disturbing our model and then we will filter data with null values for position:
\\
\clearpage
\begin{table}[]
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\textit{Index} & \textit{column name}   & \textit{Total missing} & \textit{Percent missing} \\ \hline
\textit{0}     & \textit{Position}      & \textit{60}            & \textit{0.003295}        \\ \hline
\textit{1}     & \textit{GKReflexes}    & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{2}     & \textit{Curve}         & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{...}   & \textit{...}           & \textit{...}           & \textit{...}             \\ \hline
\textit{30}    & \textit{Positioning}   & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{31}    & \textit{Interceptions} & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{32}    & \textit{Aggression}    & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{33}    & \textit{LongShots}     & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{34}    & \textit{Strength}      & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{35}    & \textit{Stamina}       & \textit{48}            & \textit{0.002636}        \\ \hline
\textit{36}    & \textit{Potential}     & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{37}    & \textit{Overall}       & \textit{0}             & \textit{0.000000}        \\ \hline
\textit{38}    & \textit{Age}           & \textit{0}             & \textit{0.000000}        \\ \hline
\end{tabular}
\caption{Missing value percent in useful attribute}
\end{table}

After handling these missing values we have 18147 rows thought, subtracting the 60 missing values.
Besides, we have to transform some $string$ type values to $int$ type, which guarantees our model works.

At last, we partition original player data according to positions, we mainly divide players into 4 positions: \textbf{Forward}, \textbf{Midfielder}, \textbf{Back}, and \textbf{Goalkeeper}.
